---
title: "Homework9"
author: "Kennedy Wendl and Vrindha Vegiraju"
date: "2023-04-14"
output: html_document
---

Github Link: https://github.com/KennedyWendl/DS202-lab2.git

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(dplyr)
library(tidyr)
library(readr)

av <- read.csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/avengers/avengers.csv", stringsAsFactors = FALSE)
av

deaths <- av %>%
  gather(key = "Time", value = "Death", 11 : 20) %>%
  mutate(Time = parse_number(Time),
         Death = if_else(Death == "", "NO", Death))

print(deaths)
```


```{r}

timeGreaterThanOne = filter(deaths, Time > 1)

filter(timeGreaterThanOne, Death == "NO")

```
Kennedy Wendl 

In the FiveThirtyEight analysis, the author mentions how superheros who have died once, have a 2/3 chance of returning. In order to check this claim, I used the filter() function from the dplyr library. I filtered Time by greater than 1 to see what superheros have died more than once. From there I filtered the Death columns to see who is still considered "dead." Of the original 1,730 superheros, 1,353 remain. I believe his claims are true. 


```{r}
library(dplyr)
grepl("die", deaths$Notes)
```
Vrindha:
They are shown or directly implied to be killed. In the FiveThirtyEight analysis, I used the grepl function to see how many deaths, if any, were included in the notes. From this, I could see the deaths present in the notes using the deaths$Notes.
